Forecasting the 2024 U.S. Presidential Election

### 2024-10-22 paper/paper.qmd
moved regression model graphs to appendix

@@

```{r}
#| echo: false
#| message: false
#| warning: false
#| label: fig-mlr-harris
#| fig-cap: Multi-Linear Regression model for Kamala Harris

# Diagnostic plots for the MLR model
par(mfrow = c(2, 2))
plot(mlr_harris_model)
par(mfrow = c(1, 1))  # Reset plot layout
```

@@

```{r}
#| echo: false
#| message: false
#| warning: false
#| label: fig-mlr-trump
#| fig-cap: Multi-Linear Regression model for Donald Trump

# Diagnostic plots for the MLR model
par(mfrow = c(2, 2))  # Set up 2x2 layout for multiple plots
plot(mlr_trump_model)  # Generates diagnostic plots: residuals, QQ plot, etc.
par(mfrow = c(1, 1))  # Reset the plot layout to normal

@@

# Check VIF for Kamala Harris model
kable(vif(mlr_harris_model), digits=3)
```

@@

```{r}
#| echo: false
#| message: false
#| warning: false
#| label: fig-harris-vif
#| fig-cap: Harris Refined Multi-Linear Regression Model

# Plot diagnostic plots for the refined model
par(mfrow = c(2, 2))
plot(mlr_harris_model_refined)
par(mfrow = c(1, 1))  # Reset plot layout
```

@@

# Check VIF for the refined model
kable(vif(mlr_harris_model_refined), digits=3)
```

@@

```{r}
#| echo: false
#| message: false
#| warning: false
#| label: fig-bbb
#| fig-cap: bbb

# Plot diagnostic plots for the stepwise model
par(mfrow = c(2, 2))
plot(step_model)
par(mfrow = c(1, 1))  # Reset layout
```

@@

>>>>

mlr_harris_model <- readRDS(here::here(("models/mlr_harris_model.rds")))
mlr_trump_model <- readRDS(here::here(("models/mlr_trump_model.rds")))
```

@@

@@

@@

# Check VIF for Kamala Harris model
kable(vif(mlr_harris_model), digits=3)

mlr_harris_model_refined <- readRDS(here::here(("models/mlr_harris_model_refined.rds")))
```

@@

@@

# Check VIF for the refined model
kable(vif(mlr_harris_model_refined), digits=3)

step_model <- step(mlr_harris_model_refined, direction = "both", trace=0)
```

@@

@@

```{r}
#| echo: false
#| message: false
#| warning: false
#| label: fig-mlr-harris
#| fig-cap: Multi-Linear Regression model for Kamala Harris
#| fig.width: 10
#| fig.height: 4

# For Harris model
par(mfrow = c(1, 2))  # Set layout for 1 row and 2 columns
plot(mlr_harris_model, which = c(1, 2))  # 1: Residuals vs Fitted, 2: Normal Q-Q
par(mfrow = c(1, 1))  # Reset plot layout

```{r}
#| echo: false
#| message: false
#| warning: false
#| label: fig-mlr-trump
#| fig-cap: Multi-Linear Regression model for Donald Trump
#| fig.width: 10
#| fig.height: 4

# For Trump model
par(mfrow = c(1, 2))  # Set layout for 1 row and 2 columns
plot(mlr_trump_model, which = c(1, 2))  # 1: Residuals vs Fitted, 2: Normal Q-Q
par(mfrow = c(1, 1))  # Reset plot layout

```{r}
#| echo: false
#| message: false
#| warning: false
#| label: fig-harris-vif
#| fig-cap: Harris Refined Multi-Linear Regression Model
#| fig.width: 10
#| fig.height: 4

# For Harris refined model
par(mfrow = c(1, 2))  # Set layout for 1 row and 2 columns
plot(mlr_harris_model_refined, which = c(1, 2))  # 1: Residuals vs Fitted, 2: Normal Q-Q
par(mfrow = c(1, 1))  # Reset plot layout

```{r}
#| echo: false
#| message: false
#| warning: false
#| label: fig-harris-step
#| fig-cap: Harris Final Multi-Linear Regression Model
#| fig.width: 10
#| fig.height: 4

# For Harris stepwise model
par(mfrow = c(1, 2))  # Set layout for 1 row and 2 columns
plot(step_model, which = c(1, 2))  # 1: Residuals vs Fitted, 2: Normal Q-Q
par(mfrow = c(1, 1))  # Reset plot layout
